\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix,epsfig,endnotes}
\usepackage{graphicx}
\usepackage{balance}
\usepackage{hyperref}

% Section references
\renewcommand{\sectionautorefname}{\S}
\renewcommand{\subsectionautorefname}{\S}

% Footnotes with symbols
\usepackage[symbol]{footmisc}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}

% In-line lists
\usepackage[inline]{enumitem}
\newlist{mylist}{enumerate*}{1}
\setlist[mylist]{label=(\roman*)}

\begin{document}

\title{Problem statement}

% No date
\date{}

\author{
{   \rm Marco Micera}\\
    Politecnico di Torino\\
    \href{mailto:marco.micera@gmail.com}{marco.micera@gmail.com}
}
\maketitle

\section*{Introduction}
This is the problem statement for my Master's thesis, which will be written at the Technische Universit{\"a}t Darmstadt, Germany, during a six-month Erasmus+ exchange and under the supervision of Prof. Patrick Eugster \footnote[2]{\label{tuda} Distributed Systems Programming Group, Technische Universit{\"a}t Darmstadt}, M.Sc. Marcel Bl{\"o}cher \footref{tuda} and Prof. Fulvio Risso \footnote[3]{\label{polito} Computer Networks Group, Politecnico di Torino}.

\section{In-network processing: a definition}
Within this project, in-network processing (INP) refers to the technique that exploits network switches to modify and/or store data packets, without involving any kind of higher-layer devices. Therefore, approaches that make use of middle-boxes do not fall within our definition of INP. This is why INP is different from \textit{active networking} and \textit{Network Function Virtualization} (NFV).

\section{Problem}
Using INP to keep scaling data centers' performance seems a promising idea: Daiet \cite{daiet} inventors claim to achieve an 86.9\%-89.3\% traffic reduction, hence reducing servers' workload; NetChain \cite{netchain} can process queries entirely in the network data plane, eliminating the query processing at servers and cutting the end-to-end latency to as little as half of an RTT.\\
Current data center Resource Managers (RMs) (e.g., Apache YARN \cite{yarn}, Google Omega \cite{omega}) are not completely network-unaware: for instance, some of them are capable of satisfying affinity rules. CloudMirror \cite{cloudmirror} even provides bandwidth guarantees to tenant applicaitons. Still, current RMs do not consider INP resources.\\
As a consequence, tenant applications cannot request INP services while asking for server resources.

\section{Modeling INP resources}
This Master's thesis goal consists in investigating how to model INP resources and how to integrate them into RMs.\\
In order to offer INP services to a tenant application, the latter should be capable of asking for INP resources through an API. To do that, INP resources must be modeled not only to support currently existing INP solutions such as \cite{daiet} \cite{netchain} \cite{incbricks} \cite{sharp}, but also to support future ones. It might be convenient to derive a single model to describe both server and INP resources.\\
Classic tenant application requests can often be modeled as a key-value data structure. CloudMirror \cite{cloudmirror} requires a \textit{Tenant Application Graph} (TAG) as an input, which is a directed graph where each vertex represents an application component and links' weights represent the minimum requested bandwidth. One possible model could be based on a TAG, describing network resources and/or INP services as vertexes or links. Tenants applications could either use the same model used within the data center or a simplified one, adding another level of abstraction.\\
Finally, a network-aware placement algorithm in the Resource Manager should then be able to allocate the requested resources accordingly.

\bibliographystyle{abbrv}
\bibliography{references}

\end{document}
